Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
Conclusions

\begin{abstract}

\end{abstract}

@@

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results}
We used various generators in our experiments.
\subsection{Print Material Characterization and Measurement}
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

@@

More ideas:
balancing bird with texture.
\section{Possible Extension}
UI to specify input deformation.
\section{Conclusion}
\section*{Acknowledgements}

>>>>

\begin{abstract}
Computational fabrication problems are often concerned with optimal material assignment. They attempt to compute a spatially varying material distribution that yields specified real-world behavior. In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms. We illustrate the utility of our framework by giving showing implemented fabrication algorithms as well as their manufactured results. 
\end{abstract}

@@

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
We used various generators in our experiments.
\subsection{Print Material Characterization and Measurement}
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

@@

More ideas:
balancing bird with texture.
%%\section{Possible Extension}
%%UI to specify input deformation.
\section{Limitations and Future Work}

\section{Conclusion}
We have presented Spec2Fab a graph based framework for building fabrication algorithms. By using the Reducer and Tuner Networks we reveal similarities between different fabrication algorithms allowing us to maximize component reuse. This both accelerates and eases implementation. We have also shown how using Spec2Fab facilitates the development and testing of new algorithms since Spec2Fab makes exploring the space of fabrication problems more efficient.
\section*{Acknowledgements}
